Validation failed EVT

### 2023-12-27 analysis/article-results.Rmd
Adding link to published url

>>>>

## Model update: logistic recalibration

```{r log-recal}
# https://darrendahly.github.io/post/homr/
mod_unpen <- glm(
  model_formula,
  family = binomial, 
  data = imps_develop
)

df_calplot_valid$lp_unpen <- predict(mod_unpen, newdata = df_calplot_valid,
                                     type = "link")

mod_recal <- glm(
  #Mc_FailedFemoralApproach ~ lp_unpen,
  #Mc_FailedFemoralApproach ~ 0 + offset(lp_valid), # same model
  #Mc_FailedFemoralApproach ~ 1 + offset(lp_valid), # Recal in the large
  #Mc_FailedFemoralApproach ~ lp_valid, # Logistic recal
  family = binomial, 
  data = df_calplot_valid
)

lp_recal <- predict(mod_recal,type = "link")
df_calplot_valid$lp_recal <- lp_recal
probs_recal <- plogis(lp_recal)
probs_grid <- seq(min(probs_recal), max(probs_recal), by = 0.005)
lp_grid <- qlogis(probs_grid)

calib_mod <- glm(
  Mc_FailedFemoralApproach ~ splines::ns(lp_recal, 5), 
  family = binomial, 
  data = df_calplot_valid, 
  weights = df_calplot_valid$wts
)

stacked_df <- data.frame(
    "predicted" = probs_grid,
    "observed" = predict(calib_mod, newdata = data.frame("lp_recal" = lp_grid), type = "response")
)

ggplot() +
  geom_line(
      data = stacked_df,
      aes(x = predicted, y = observed),
      size = 2
    ) +
  geom_abline(
      intercept = 0,
      slope = 1, col = "red", size = 1, linetype = "dashed"
    ) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
```
